Stellar Migration and Chemical Enrichment in the Milky Way Disc: A Hybrid Model

### 2021-10-01 chemev/MWbimodality/paper/draft3/methods.tex
paper updates

\section{Methods} 
\label{sec:methods} 
To fulfill the goals of this paper, we develop and make use of newly released 
features within the~\texttt{Versatile Integrator for Chemical Evolution} 
(\vice;~\citealp{Johnson2020}), an open-source~\texttt{python} package 
available for~\texttt{Unix} system architectures (for further details, see 
Appendix~\ref{sec:vice}). 
These features are designed to handle models such as these with a wide range of 
flexibility. 
We reserve a description of~\vice's migration algorithm and our simulation 
parameters for~\S~\ref{sec:methods:migration}, first describing our sample of 
star particles from the hydrodynamic simulation. 
\par 
Although we make use of a hydrodynamic simulation to drive stellar migration, 
we do~\textit{not} make use of its SFH. 
While our study employs similar techniques as~\citet{Minchev2013}, ours differs 
slightly in that they take a single SFH which is similar, but not identical to 
that of their N-body+SPH simulation; in this paper we present a handful of 
assumptions about the SFH, which do not necessarily resemble that of~\hsim. 
An alternative to modeling radial migration based on a 
hydrodynamical simulation is to invoke dynamical arguments; 
\citet{Schoenrich2009a} and~\citet{Sharma2020} take such an approach. 
This method, however, introduces free parameters which then require fitting to 
data. 
An advantage of our technique is that there are no free parameters describing 
radial migration introduced to the model; it is unclear how much 
fitting radial migration parameters could bias the model into agreement with 
parts of the data not involved in the fitting process. 
Instead we adopt a physically motivated migration model evolved from 
cosmological initial conditions. 
We rely on a single realization of this numerical model and are thus subject to 
the differences between the dynamical history of this simulated galaxy and that 
of the Milky Way. 
However, one could compare the predictions made by our chemical evolution 
models when applied to different hydrodynamical simulations, a direction we 
plan to pursue in future work. 
We emphasize that the hydrodynamical simulation~\textit{only} informs the 
mixing processes in our models, and there is no N-body integration involved in 
our models aside from that which was used to run the~\hsim~simulation in the 
first place. 
{\color{red} 
A summary of our chemical evolution model parameters can be found in 
Table~\ref{tab:params}. 
}

@@

{\color{red}\textit{

@@

}}

@@

This stellar population then adopts the {\color{red} present day midplane 
distance~$z$ and the} change in orbital radius 

@@

{\color{red} 

@@

@@

and large~$\rgal$ where {\color{red} only a small fraction of~\hsim's star 
particles reside,} 

@@

\subsection{Star Formation Histories} 
\label{sec:methods:sfhs} 
\vice~computes models in either ``infall'', ``star formation'', or ``gas'' 
mode, referring to which component of the evolutionary history the user has 
specified. 
The starburst models of~\citet{Johnson2020} ran in infall mode, 
meaning that the gas infall rate is specified and the SFR follows from the gas 
surface density and adopted star formation law. 
Here we run~\vice~in star formation mode so that we achieve a specified form of 
the SFHs in our models. 
In Appendix~\ref{sec:normalize_sfh}, we explain how we normalize the parameters 
of our SFHs to produce a realistic model Galaxy at the present day. 
In short, we take a unitless description of the time-dependence of the SFH at a 
given Galactocentric radius, denoted~$f(t|\rgal)$, and a unitless description 
of the present day stellar surface density gradient, denoted~$g(\rgal)$. 
We integrate~$f(t|\rgal)$ with time for each annulus, assuming~$\rgal$ to 
correspond to the centre of the zone, and attach a prefactor to 
$f(t|\rgal)$ in each annulus such that the desired gradient is achieved 
with a total stellar mass similar to the Milky Way. 
This procedure neglects the impact of radial migration, assuming that it does 
not significantly alter the form of~$g(\rgal)$. 
{\color{red} 
We find this to be true for our sample of~\hsim~star particles, and we 
demonstrate that this assumption holds in our chemical evolution models 
in~\S~\ref{sec:methods:surface_density_gradient}, where we also detail our 
adopted form of~$g(\rgal)$. 
}
% We demonstrate that this assumption holds 
% in~\S~\ref{sec:methods:surface_density_gradient}, in which we also detail our 
% adopted form of~$g(\rgal)$. 
The equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
calculate these prefactors for alternative models of Milky Way-like galaxies. 
\par 
In the present paper, we consider four forms of the SFH, which we dub 
``constant'', ``inside-out'', ``late-burst'', and ``outer-burst''. 
They are defined as follows: 
\begin{itemize} 
	\item \textbf{Constant}: The SFH at a given radius is time-independent, 
	\begin{equation} 
	f_\text{C}(t|\rgal) = 1. 
	\label{eq:constant_sfh} 
	\end{equation} 
	This case is of theoretical interest because it quantifies the effect of 
	stellar migration while removing the impact of a time-dependent SFH.

	\item \textbf{Inside-Out}: This is our fiducial SFH, 
	\begin{equation} 
	f_\text{IO}(t|\rgal) = (1 - e^{-t / \tau_\text{rise}}) 
	e^{-t / \tau_\text{sfh}}. 
	\label{eq:insideout_sfh} 
	\end{equation} 
	We adopt this mathematical form over the somewhat more common 
	$te^{-t/\tau_\text{sfh}}$ because it allows separate control over the 
	rising and falling phase of the SFH. 
	Equation~\refp{eq:insideout_sfh} has a maximum near~$\tau_\text{rise}$, 
	which in this paper we set to 2 Gyr at all radii. 
	This form produces a peak in star formation at lookback times of~$\sim$11 
	Gyr, roughly corresponding to a redsfhit of~$z \approx$ 2.5. 
	{\color{red} 
	In detail, however, the time of peak star formation increases 
	with~$\tau_\text{sfh}$, which in turn increases with~\rgal~in our models 
	(see discussion below). 
	As a result,~$\dot{\Sigma}_\star$ in the outer disc instead reaches its 
	peak at lookback times of~$\sim$7 - 8 Gyr, qualitatively consistent with 
	the radial growth of disc galaxies~\citep{Bird2013, Bird2021, Frankel2019}. 
	} 
	% We discuss the choice of~$\tau_\text{sfh}$ below.

@@

The inside-out model is our fiducial choice, and it is the model shown in 
figures unless otherwise specified. 
The constant SFR model allows us to investigate the impact of migration when 
the time-dependence of the SFH is removed, and the two burst models allow us to 
explore the consequences of elevated recent star formation supported by some 
recent data. 
{\color{red} 
More complex scenarios, such as multiple bursts induced by repeated satellite 
passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} or 
the onset of star formation occurring later in the outer disc to better capture 
the radial growth of the Galaxy~\citep[e.g.][]{Frankel2019}, can be 
explored easily using~\vice, but we do not explore such models here. 
} 
% More complex scenarios with multiple bursts induced by repeated satellite 
% passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} 
% can be modeled easily in~\vice, but we do not explore them here. 
\par 
We derive the~$\tau_\text{sfh}-\rgal$ relation from the data of 
\citet{Sanchez2020}, who presents the stellar surface density~$\Sigma_\star$ as 
a function of age in bins of~$R/R_\text{e}$ for MaNGA 
galaxies~\citep{Bundy2015}, where $R_\text{e}$ is the half-light radius. 
Here we take the~$M_\star = 10^{10.5} - 10^{11}~\msun$~bin for Sa/Sb spirals 
and simultaneously fit the normalization and e-folding timescale 
$\tau_\text{sfh}$ of our~$f_\text{IO}(t|\rgal)$ form to the data. 
Although the normalization is irrelevant to our models and determined via the 
method outlined in Appendix~\ref{sec:normalize_sfh}, we adopt the resulting 
$\tau_\text{sfh}-\rgal$ relation in our models. 
Our adopted stellar surface density gradient 
(see~\S~\ref{sec:methods:surface_density_gradient}) implies a present-day 
half-mass radius near 4 kpc. 
The findings of~\citet{Garcia-Benito2017} and~\citet{GonzalezDelgado2014} 
suggest that half-light radii are marginally larger than half-mass radii. 
Based on equation (4) of~\citet{GonzalezDelgado2014} relating the two for 
circular apertures, we expect our model Galaxy to have a 
half-light radius near 5 kpc. 
We therefore adopt~$R_\text{e}$ = 5 kpc to convert the 
$\tau_\text{sfh}-\rgal/R_\text{e}$ relation resulting from our fit to the 
\citet{Sanchez2020} data into a~$\tau_\text{sfh}-\rgal$ relation. 
\par 
We illustrate this relationship in the bottom panel of Fig. 
\ref{fig:eta_tau_sfh}. 
The resulting timescales are long, particularly for the outer Galaxy. 
With a red dotted line, we highlight a value of~$\tau_\text{sfh} \approx$~15 
Gyr at an assumed orbital radius of the sun of $R_\odot$ = 8 kpc. 
The long timescales reflect the fact that the 
$\Sigma_\star(\tau_\text{lookback})$ profiles in Fig. 11 of~\citet{Sanchez2020} 
are fairly flat. 
For comparison, we have also considered the assumption that the Galactic SFH 
may have resembled the cosmic SFH by running models with e-folding timescales 
of a~$\sim$few Gyr~\citep[e.g.][]{Madau2014}. 
We find similar results in these cases, suggesting that our qualitative 
conclusions are not sensitive to the exact values of~$\tau_\text{sfh}$.

We plot the resulting SFHs of our models in the top row of Fig.~\ref{fig:evol} 
for a handful of radii. 
Because of the long~$\tau_\text{sfh}$, the SFR at most radii has fallen only 
modestly from its 2 Gyr peak in the inside-out model. 
{\color{red} 
The gas supply, whose value at all timesteps is known via the star formation 
efficiency timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), is 
illustrated in the bottom row of Fig.~\ref{fig:evol}. 
}
% At all timesteps, the gas supply is known via the star formation efficiency 
% timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), which is illustrated in 
% the bottom row of Fig.~\ref{fig:evol}. 
\vice~automatically calculates the implied infall rate by comparing the amount 
of gas lost to outflows and star formation in a given timestep to that which is 
required to sustain the user-specified level of star formation at the next 
timestep; we assume the infalling gas to be of zero metallicity at all times. 
This quantity is shown in the middle row of Fig.~\ref{fig:evol}.

@@

% As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
% presents the recipe by which we select a unitless function describing the 
% stellar surface density gradient~$g(\rgal)$. 
{\color{red} 
As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
presents the recipe by which we normalize our star formation histories, a 
necessary component of which is a unitless function describing the stellar 
surface density gradient~$g(\rgal)$. 
}
In setting the normalization, our model ensures that the integral of~$g(\rgal)$ 
over the surface area of the disc predicts a total stellar mass in agreement 
with that observed for the Milky Way. 
For this value, we adopt~$M_\star^\text{MW} = 5.17~\times~10^{10}~\msun$ from 
\citet[][$\pm 1.11\times10^{10}~\msun$]{Licquia2015}. 
This is the total disc mass only; when the bulge is included, the total 
becomes~$(6.08~\pm~1.17)~\times~10^{10}~\msun$. 
Since we are modeling only the disc populations here, we omit the contribution 
from the bulge to the total mass budget. 
% For this value, we adopt 
% $M_\star^\text{MW} = (5.17 \pm 1.11)\times10^{10}$~\msun~\citep{Licquia2015}. 
% This is the total disc mass of the Galaxy;~\citet{Licquia2015} report 
% $(6.08 \pm 1.17)\times10^{10}~\msun$~when the bulge is considered. 
% Since we are modeling only the disc populations here, we omit the contribution 
% the bulge would have to the total mass budget. 
% This is the total stellar mass of the Galaxy, including the bulge; 
% \citet{Licquia2015} report~$(5.17 \pm 1.11)\times10^{10}$~\msun~as the mass of 
% the disc alone. 
% Although we are not modeling the bulge here, our model extends to~$\rgal$ = 0 
% and our sample of candidate analogue star particles from~\hsim includes those 
% with bulge-like kinematics. 
\par 
We adopt a double exponential form for~$g(\rgal)$, describing the thin and 
thick disc components of the Galaxy: 
\begin{equation} 
g(\rgal) = e^{-\rgal/R_t} + \frac{\Sigma_T}{\Sigma_t} 
e^{-\rgal/R_T}~, 
\label{eq:gradient} 
\end{equation} 
where~$R_t$~and~$R_T$~are the scale radii of the thin and thick discs, 
respectively, and~$\Sigma_T/\Sigma_t$~is the ratio of their surface densities 
at~$\rgal$~= 0. 
We adopt~$R_t$~= 2.5 kpc,~$R_T$~= 2.0 kpc, and~$\Sigma_T/\Sigma_t$~= 0.27 based 
on the findings of~\citet{Bland-Hawthorn2016}. 
We plot the single exponential forms of each disc component as dotted black 
lines in Fig.~\ref{fig:surface_density}, with the solid black line denoting the 
sum of the two.

@@

We plot the resultant surface density gradients from our fiducial, inside-out 
SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
stellar gradient and the gas in blue. 
The stellar gradient very nearly follows our target gradient (equation 
\ref{eq:gradient}) denoted by the solid black line. 
{\color{red} 
Simply introducing scatter around the adopted trend, stellar migration has 
not significantly altered the overall form of the gradient, as we assumed in 
Appendix~\ref{sec:normalize_sfh}. 
We find this to also be true for our sample of star particles from~\hsim, 
a result which is expected given the roughly symmetric shapes of the 
histograms in the top row of Fig.~\ref{fig:h277_decomposition} and consistent 
with previous arguments that radial migration does not significantly alter the 
vertical and radial structure of the disc~\citep[e.g.][]{Sellwood2014, 
VeraCiro2014}. 
}
% Stellar migration has not altered the overall form of the gradient, simply 
% introducing scatter around the adopted trend. 
Although there are slight enhancements at small~$\rgal$ and deficits at large 
$\rgal$, the agreement is excellent in the regions of the Galaxy where the 
gradient is best constrained observationally. 
The~$\rgal$ > 15.5 kpc populations are composed entirely of stars that 
migrated there, since that is the radius at which we shut off star formation. 
The gas gradient shows a break in the scale radius near~$\rgal \approx$ 
6 kpc. This is a consequence of our adopted star formation law; at 
$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). 
\par 
Although we adopt the~\citet{Licquia2015} disc stellar mass of the Milky Way 
here, we find similar results when taking a value which differs even by an 
order of magnitude. 
If we used a linear star formation law, then our chemical evolution would be 
independent of the mass normalization as it is in corresponding one-zone 
models (\citealp*{Spitoni2017};~\citealp{Weinberg2017, Belfiore2019}). 
The mass normalization enters our calculation because it affects the transition 
between the linear and non-linear regimes of our star formation law 
(equation~\ref{eq:sf_law}), but the impact on abundance evolution is minimal.

>>>>

\section{Methods} 
\label{sec:methods} 
To fulfill the goals of this paper, we develop and make use of newly released 
features within the~\texttt{Versatile Integrator for Chemical Evolution} 
(\vice;~\citealp{Johnson2020}), an open-source~\texttt{python} package 
available for~\texttt{Unix} system architectures (for further details, see 
Appendix~\ref{sec:vice}). 
These features are designed to handle models such as these with a wide range of 
flexibility. 
We reserve a description of~\vice's migration algorithm and our simulation 
parameters for~\S~\ref{sec:methods:migration}, first describing our sample of 
star particles from the hydrodynamic simulation. 
\par 
Although we make use of a hydrodynamic simulation to drive stellar migration, 
we do~\textit{not} make use of its SFH. 
While our study employs similar techniques as~\citet{Minchev2013}, ours differs 
slightly in that they take a single SFH which is similar, but not identical to 
that of their N-body+SPH simulation; in this paper we present a handful of 
assumptions about the SFH, which do not necessarily resemble that of~\hsim. 
An alternative to modeling radial migration based on a 
hydrodynamical simulation is to invoke dynamical arguments; 
\citet{Schoenrich2009a} and~\citet{Sharma2020} take such an approach. 
This method, however, introduces free parameters which then require fitting to 
data. 
An advantage of our technique is that there are no free parameters describing 
radial migration introduced to the model; it is unclear how much 
fitting radial migration parameters could bias the model into agreement with 
parts of the data not involved in the fitting process. 
Instead we adopt a physically motivated migration model evolved from 
cosmological initial conditions. 
We rely on a single realization of this numerical model and are thus subject to 
the differences between the dynamical history of this simulated galaxy and that 
of the Milky Way. 
However, one could compare the predictions made by our chemical evolution 
models when applied to different hydrodynamical simulations, a direction we 
plan to pursue in future work. 
We emphasize that the hydrodynamical simulation~\textit{only} informs the 
mixing processes in our models, and there is no N-body integration involved in 
our models aside from that which was used to run the~\hsim~simulation in the 
first place. 
% {\color{red} 
A summary of our chemical evolution model parameters can be found in 
Table~\ref{tab:params}. 
% }

@@

% {\color{red}
\textit{

@@

% }

@@

This stellar population then adopts the %{\color{red} 
present day midplane 
distance~$z$ and the
%} 
change in orbital radius 

@@

% {\color{red} 

@@

% }

@@

and large~$\rgal$ where %{\color{red} 
only a small fraction of~\hsim's star 
particles reside,
% } 

@@

\subsection{Star Formation Histories} 
\label{sec:methods:sfhs} 
\vice~computes models in either ``infall'', ``star formation'', or ``gas'' 
mode, referring to which component of the evolutionary history the user has 
specified. 
The starburst models of~\citet{Johnson2020} ran in infall mode, 
meaning that the gas infall rate is specified and the SFR follows from the gas 
surface density and adopted star formation law. 
Here we run~\vice~in star formation mode so that we achieve a specified form of 
the SFHs in our models. 
In Appendix~\ref{sec:normalize_sfh}, we explain how we normalize the parameters 
of our SFHs to produce a realistic model Galaxy at the present day. 
In short, we take a unitless description of the time-dependence of the SFH at a 
given Galactocentric radius, denoted~$f(t|\rgal)$, and a unitless description 
of the present day stellar surface density gradient, denoted~$g(\rgal)$. 
We integrate~$f(t|\rgal)$ with time for each annulus, assuming~$\rgal$ to 
correspond to the centre of the zone, and attach a prefactor to 
$f(t|\rgal)$ in each annulus such that the desired gradient is achieved 
with a total stellar mass similar to the Milky Way. 
This procedure neglects the impact of radial migration, assuming that it does 
not significantly alter the form of~$g(\rgal)$. 
% {\color{red} 
We find this to be true for our sample of~\hsim~star particles, and we 
demonstrate that this assumption holds in our chemical evolution models 
in~\S~\ref{sec:methods:surface_density_gradient}, where we also detail our 
adopted form of~$g(\rgal)$. 
% }
% We demonstrate that this assumption holds 
% in~\S~\ref{sec:methods:surface_density_gradient}, in which we also detail our 
% adopted form of~$g(\rgal)$. 
The equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
calculate these prefactors for alternative models of Milky Way-like galaxies. 
\par 
In the present paper, we consider four forms of the SFH, which we dub 
``constant'', ``inside-out'', ``late-burst'', and ``outer-burst''. 
They are defined as follows: 
\begin{itemize} 
	\item \textbf{Constant}: The SFH at a given radius is time-independent, 
	\begin{equation} 
	f_\text{C}(t|\rgal) = 1. 
	\label{eq:constant_sfh} 
	\end{equation} 
	This case is of theoretical interest because it quantifies the effect of 
	stellar migration while removing the impact of a time-dependent SFH.

	\item \textbf{Inside-Out}: This is our fiducial SFH, 
	\begin{equation} 
	f_\text{IO}(t|\rgal) = (1 - e^{-t / \tau_\text{rise}}) 
	e^{-t / \tau_\text{sfh}}. 
	\label{eq:insideout_sfh} 
	\end{equation} 
	We adopt this mathematical form over the somewhat more common 
	$te^{-t/\tau_\text{sfh}}$ because it allows separate control over the 
	rising and falling phase of the SFH. 
	Equation~\refp{eq:insideout_sfh} has a maximum near~$\tau_\text{rise}$, 
	which in this paper we set to 2 Gyr at all radii. 
	This form produces a peak in star formation at lookback times of~$\sim$11 
	Gyr, roughly corresponding to a redsfhit of~$z \approx$ 2.5. 
	% {\color{red} 
	In detail, however, the time of peak star formation increases 
	with~$\tau_\text{sfh}$, which in turn increases with~\rgal~in our models 
	(see discussion below). 
	As a result,~$\dot{\Sigma}_\star$ in the outer disc instead reaches its 
	peak at lookback times of~$\sim$7 - 8 Gyr, qualitatively consistent with 
	the radial growth of disc galaxies~\citep{Bird2013, Bird2021, Frankel2019}. 
	% } 
	% We discuss the choice of~$\tau_\text{sfh}$ below.

@@

The inside-out model is our fiducial choice, and it is the model shown in 
figures unless otherwise specified. 
The constant SFR model allows us to investigate the impact of migration when 
the time-dependence of the SFH is removed, and the two burst models allow us to 
explore the consequences of elevated recent star formation supported by some 
recent data. 
% {\color{red} 
More complex scenarios, such as multiple bursts induced by repeated satellite 
passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} or 
the onset of star formation occurring later in the outer disc to better capture 
the radial growth of the Galaxy~\citep[e.g.][]{Frankel2019}, can be 
explored easily using~\vice, but we do not explore such models here. 
% } 
% More complex scenarios with multiple bursts induced by repeated satellite 
% passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} 
% can be modeled easily in~\vice, but we do not explore them here. 
\par 
We derive the~$\tau_\text{sfh}-\rgal$ relation from the data of 
\citet{Sanchez2020}, who presents the stellar surface density~$\Sigma_\star$ as 
a function of age in bins of~$R/R_\text{e}$ for MaNGA 
galaxies~\citep{Bundy2015}, where $R_\text{e}$ is the half-light radius. 
Here we take the~$M_\star = 10^{10.5} - 10^{11}~\msun$~bin for Sa/Sb spirals 
and simultaneously fit the normalization and e-folding timescale 
$\tau_\text{sfh}$ of our~$f_\text{IO}(t|\rgal)$ form to the data. 
Although the normalization is irrelevant to our models and determined via the 
method outlined in Appendix~\ref{sec:normalize_sfh}, we adopt the resulting 
$\tau_\text{sfh}-\rgal$ relation in our models. 
Our adopted stellar surface density gradient 
(see~\S~\ref{sec:methods:surface_density_gradient}) implies a present-day 
half-mass radius near 4 kpc. 
The findings of~\citet{Garcia-Benito2017} and~\citet{GonzalezDelgado2014} 
suggest that half-light radii are marginally larger than half-mass radii. 
Based on equation (4) of~\citet{GonzalezDelgado2014} relating the two for 
circular apertures, we expect our model Galaxy to have a 
half-light radius near 5 kpc. 
We therefore adopt~$R_\text{e}$ = 5 kpc to convert the 
$\tau_\text{sfh}-\rgal/R_\text{e}$ relation resulting from our fit to the 
\citet{Sanchez2020} data into a~$\tau_\text{sfh}-\rgal$ relation. 
\par 
We illustrate this relationship in the bottom panel of Fig. 
\ref{fig:eta_tau_sfh}. 
The resulting timescales are long, particularly for the outer Galaxy. 
With a red dotted line, we highlight a value of~$\tau_\text{sfh} \approx$~15 
Gyr at an assumed orbital radius of the sun of $R_\odot$ = 8 kpc. 
The long timescales reflect the fact that the 
$\Sigma_\star(\tau_\text{lookback})$ profiles in Fig. 11 of~\citet{Sanchez2020} 
are fairly flat. 
For comparison, we have also considered the assumption that the Galactic SFH 
may have resembled the cosmic SFH by running models with e-folding timescales 
of a~$\sim$few Gyr~\citep[e.g.][]{Madau2014}. 
We find similar results in these cases, suggesting that our qualitative 
conclusions are not sensitive to the exact values of~$\tau_\text{sfh}$.

We plot the resulting SFHs of our models in the top row of Fig.~\ref{fig:evol} 
for a handful of radii. 
Because of the long~$\tau_\text{sfh}$, the SFR at most radii has fallen only 
modestly from its 2 Gyr peak in the inside-out model. 
% {\color{red} 
The gas supply, whose value at all timesteps is known via the star formation 
efficiency timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), is 
illustrated in the bottom row of Fig.~\ref{fig:evol}. 
% }
% At all timesteps, the gas supply is known via the star formation efficiency 
% timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), which is illustrated in 
% the bottom row of Fig.~\ref{fig:evol}. 
\vice~automatically calculates the implied infall rate by comparing the amount 
of gas lost to outflows and star formation in a given timestep to that which is 
required to sustain the user-specified level of star formation at the next 
timestep; we assume the infalling gas to be of zero metallicity at all times. 
This quantity is shown in the middle row of Fig.~\ref{fig:evol}.

@@

% As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
% presents the recipe by which we select a unitless function describing the 
% stellar surface density gradient~$g(\rgal)$. 
% {\color{red} 
As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
presents the recipe by which we normalize our star formation histories, a 
necessary component of which is a unitless function describing the stellar 
surface density gradient~$g(\rgal)$. 
% }
In setting the normalization, our model ensures that the integral of~$g(\rgal)$ 
over the surface area of the disc predicts a total stellar mass in agreement 
with that observed for the Milky Way. 
For this value, we adopt~$M_\star^\text{MW} = 5.17~\times~10^{10}~\msun$ from 
\citet[][$\pm 1.11\times10^{10}~\msun$]{Licquia2015}. 
This is the total disc mass only; when the bulge is included, the total 
becomes~$(6.08~\pm~1.17)~\times~10^{10}~\msun$. 
Since we are modeling only the disc populations here, we omit the contribution 
from the bulge to the total mass budget. 
% For this value, we adopt 
% $M_\star^\text{MW} = (5.17 \pm 1.11)\times10^{10}$~\msun~\citep{Licquia2015}. 
% This is the total disc mass of the Galaxy;~\citet{Licquia2015} report 
% $(6.08 \pm 1.17)\times10^{10}~\msun$~when the bulge is considered. 
% Since we are modeling only the disc populations here, we omit the contribution 
% the bulge would have to the total mass budget. 
% This is the total stellar mass of the Galaxy, including the bulge; 
% \citet{Licquia2015} report~$(5.17 \pm 1.11)\times10^{10}$~\msun~as the mass of 
% the disc alone. 
% Although we are not modeling the bulge here, our model extends to~$\rgal$ = 0 
% and our sample of candidate analogue star particles from~\hsim includes those 
% with bulge-like kinematics. 
\par 
We adopt a double exponential form for~$g(\rgal)$, describing the thin and 
thick disc components of the Galaxy: 
\begin{equation} 
g(\rgal) = e^{-\rgal/R_t} + \frac{\Sigma_T}{\Sigma_t} 
e^{-\rgal/R_T}~, 
\label{eq:gradient} 
\end{equation} 
where~$R_t$~and~$R_T$~are the scale radii of the thin and thick discs, 
respectively, and~$\Sigma_T/\Sigma_t$~is the ratio of their surface densities 
at~$\rgal$~= 0. 
We adopt~$R_t$~= 2.5 kpc,~$R_T$~= 2.0 kpc, and~$\Sigma_T/\Sigma_t$~= 0.27 based 
on the findings of~\citet{Bland-Hawthorn2016}. 
We plot the single exponential forms of each disc component as dotted black 
lines in Fig.~\ref{fig:surface_density}, with the solid black line denoting the 
sum of the two.

@@

We plot the resultant surface density gradients from our fiducial, inside-out 
SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
stellar gradient and the gas in blue. 
The stellar gradient very nearly follows our target gradient (equation 
\ref{eq:gradient}) denoted by the solid black line. 
% {\color{red} 
Simply introducing scatter around the adopted trend, stellar migration has 
not significantly altered the overall form of the gradient, as we assumed in 
Appendix~\ref{sec:normalize_sfh}. 
We find this to also be true for our sample of star particles from~\hsim, 
a result which is expected given the roughly symmetric shapes of the 
histograms in the top row of Fig.~\ref{fig:h277_decomposition} and consistent 
with previous arguments that radial migration does not significantly alter the 
vertical and radial structure of the disc~\citep[e.g.][]{Sellwood2014, 
VeraCiro2014}. 
% }
% Stellar migration has not altered the overall form of the gradient, simply 
% introducing scatter around the adopted trend. 
Although there are slight enhancements at small~$\rgal$ and deficits at large 
$\rgal$, the agreement is excellent in the regions of the Galaxy where the 
gradient is best constrained observationally. 
The~$\rgal$ > 15.5 kpc populations are composed entirely of stars that 
migrated there, since that is the radius at which we shut off star formation. 
The gas gradient shows a break in the scale radius near~$\rgal \approx$ 
6 kpc. This is a consequence of our adopted star formation law; at 
$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). 
\par 
Although we adopt the~\citet{Licquia2015} disc stellar mass of the Milky Way 
here, we find similar results when taking a value which differs even by an 
order of magnitude. 
If we used a linear star formation law, then our chemical evolution would be 
independent of the mass normalization as it is in corresponding one-zone 
models (\citealp*{Spitoni2017};~\citealp{Weinberg2017, Belfiore2019}). 
The mass normalization enters our calculation because it affects the transition 
between the linear and non-linear regimes of our star formation law 
(equation~\ref{eq:sf_law}), but the impact on abundance evolution is minimal.
